Formalization and Automated Verification of \\ G\"{o}del's Proof of God's Existence\thanks{This work has been supported by the German Research Foundation under grant BE2501/9-1.}

### 2013-09-13 Abstract/Square/GodProof-Abstract-SquareVersion.tex
further reduction to 1 page

The following has been done (and in this order):\footnote{System URLs:
 TPTP---\url{http://tptp.org};
 Nitpick---\url{http://www4.in.tum.de/\~{}blanchet/nitpick.html};
 LEO-II---\url{http://leoprover.org};
 Satallax---\url{http://www.ps.uni-saarland.de/~cebrown/satallax/}; 
 Coq---\url{http://coq.inria.fr};
 Isabelle---\url{http://isabelle.in.tum.de}.
}
(i) a detailed natural deduction proof;
%
(ii) a formalization in TPTP THF syntax;
%
(iii) an automatic verification of the consistency of the axioms and 
definitions with Nitpick;
%
(iv) an automatic demonstration of the theorems with the provers LEO-II and Satallax;
%
(v) a step-by-step formalization using the Coq proof assistant;
%
(vi) a formalization using the Isabelle proof assistant, where the
theorems (and some additional lemmata) have been automated with the
Isabelle tools Sledgehammer and Metis.

@@

In our ongoing computer-assisted study of G\"odel's proof our proof
tools have made
some interesting observations, including:
(a) The basic modal logic K is sufficient for proving the first three
theorems (T1, Coro and T2) as outlined in Scott's notes.
(b)  For proving the final theorem (T3), logic KB is
  sufficient.
(c) G\"odel's original  version of the proof \cite{GoedelNotes}, which omits
conjunct $\phi(x)$ in definition of \textit{essence}, seems inconsistent.
% (d) for proving theorem T1, only the left to right direction of
%   axiom A1 is needed. However, the backward direction of A1 is
%   required for proving T2.
% \end{itemize}

>>>>

The following has been done (and in this order):\footnote{System URLs:
 TPTP---\url{http://tptp.org};
 Nitpick---\url{http://www4.in.tum.de/\~{}blanchet/nitpick.html};
 LEO-II---\url{http://leoprover.org};
 Satallax---\url{http://www.ps.uni-saarland.de/\~{}cebrown/satallax}; 
 Coq---\url{http://coq.inria.fr};
 Isabelle---\url{http://isabelle.in.tum.de}.
}
(i) a detailed natural deduction proof;
%
(ii) a formalization in TPTP THF syntax;
%
(iii) an automatic verification of the consistency of the axioms and 
definitions with Nitpick;
%
(iv) an automatic demonstration of the theorems with the provers LEO-II and Satallax;
%
(v) a step-by-step formalization using the Coq proof assistant;
%
(vi) a formalization using the Isabelle proof assistant, where the
theorems (and some additional lemmata) have been automated with the
Isabelle tools Sledgehammer and Metis.

@@

In our ongoing computer-assisted study of G\"odel's proof our proof
tools have made
some interesting observations, including:
(a) The basic modal logic K is sufficient for proving the first three
theorems (T1, Coro and T2) as outlined in Scott's notes.
(b)  For proving the final theorem (T3), logic KB is
  sufficient.
(c) G\"odel's original  version of the proof \cite{GoedelNotes}, which omits
conjunct $\phi(x)$ in definition of \emph{essence}, seems inconsistent.
% (d) for proving theorem T1, only the left to right direction of
%   axiom A1 is needed. However, the backward direction of A1 is
%   required for proving T2.
% \end{itemize}
